Check experimental design

### 2019-05-22 analysis/01_check-design.Rmd
Changed language of 7-point scales from left to right to 1 to 7 (since its vertical on mobile)

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

@@

```{r}
# Convert the attributes in design into factors
dummy_design <- as.data.frame(design)
for(i in 4:ncol(dummy_design)) {
  dummy_design[,i] <- as.factor(dummy_design[,i])
}

>>>>

```{r check-design, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

@@

```{r check-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
dummy_design <- as.data.frame(design)
for(i in 4:ncol(dummy_design)) {
  dummy_design[,i] <- as.factor(dummy_design[,i])
}
